The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-04-14 paper/paper.tex
caption update

\begin{figure*}[htbp]
% \centering
\includegraphics[width=0.9\linewidth]{results/nzoverlap_dc2_funbins.pdf}
\caption{The fraction of total objects assigned to each tomographic bin that are ambiguously assigned, for 
the \textsc{funbins} tomograph method and three choices of bands.  The $x$- and $y$-axes 
show tomographic bin indices, 
and the color represents the fraction of objects (compared to the total number in the challenge) that are 
at redshifts dominated by different tomographic to the ones they are assigned.  This metric corresponds to
the fraction of the area that is shaded in two colours in Figure \ref{fig:funbin_nz}.
The total-overlap figure gives the total fraction of objects
that are ambiguous over all bins, and is the sum of all the grid values.}
\label{fig:overlap}
\end{figure*}

>>>>

\begin{figure*}[htbp]
% \centering
\includegraphics[width=0.9\linewidth]{results/nzoverlap_dc2_funbins.pdf}
\caption{The pairwise fractions of total objects in redshift regions where multiple tomographic bins contain galaxies, for 
the \textsc{funbins} tomography method and three choices of bands.  
The $x$- and $y$-axes 
show tomographic bin indices, 
and the color represents the fraction of objects (compared to the total number in the challenge) that are 
at redshifts where both tomographic bins have members, in bins of width $\delta z=10^{-3}$.  
This metric corresponds to
the fraction of the area that is shaded in two colours in Figure \ref{fig:funbin_nz}.
The total-overlap figure gives the total fraction of objects
that are ambiguous over all bins, and is the sum of all the pairwise values.}
\label{fig:overlap}
\end{figure*}
